Music adaptation: Analysis

### 2022-12-01 analysis/baseline.Rmd
implement order to vel/vel-diff
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

vel <- vel_trial[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(SubNr, Articulation, Dynamics, Category, Subcomponent2)]
setorder(vel, "Subcomponent2", "SubNr", "Dynamics", "Articulation", "Category")
vel
```

@@

vel_diff <- vel_diff_trial[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(SubNr, Articulation, Dynamics, Category, Subcomponent2)]
setorder(vel_diff, "SubNr", "Dynamics", "Articulation", "Category")
vel_diff
```

>>>>

vel <- vel_trial[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(SubNr, Articulation, Dynamics, Category, Subcomponent2)]
setorder(vel, "SubNr", "Subcomponent2", "SubNr", "Dynamics", "Articulation", "Category")
vel
```

@@

vel_diff <- vel_diff_trial[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(SubNr, Articulation, Dynamics, Category, Subcomponent2)]
setorder(vel_diff, "SubNr", "Subcomponent2", "Dynamics", "Articulation", "Category")
vel_diff
```
